The connection between star formation rate and dark matter halo mass during reionization

### 2015-08-17 paper/ms.tex
adding some text and making minor corrections

\title{The connection between star formation rate and dark matter halo
  mass in the epoch of reionization}  
\shorttitle{SFR and DM halo mass during reionization}

@@

\keywords{galaxies: high-redshift --- methods: numerical} 
\begin{abstract}
We present updated constraints on the relationship between the star
formation rate and dark matter halo mass at redshift $z\sim 6$.
The observational basis for our work is the restframe UV luminosity
function data obtained with HST, CFHTLS, Subary and UKIRT.
The constraints are based on an abundance matching methodology to the
observational data using cosmological N-body simulations.
The relationship between halo mass and star formation rate follows a
double power law.
We also take into account the influence on the results of the dust extinction
scaling derived from observations by Bouwens et al. (2012).
Taking advantage of a wide dynamical range in observations and
simulations we manage to constrain the free parameters of our model
for halos in the mass range $10^{10}\Msun < M_{h}<10^{13}\Msun$. 
We find that including dust extinction improves the the match with
observations.
Finally, we compare these results against the prediction of abundance matching
methods (to the stellar mass), a semi-analytic model of galaxy
formation (GALFORM) and a hydrodynamical simulation (Illustris).
\end{abstract}

@@

We use information compiled in four different publications. 
All of them select galaxy candidates at $z\sim 6$ using the drop-out
technique \citep{Steidel96}.  
In what follows we describe the relevant details of each reference.

\subsection{Bouwens et al. 2015}
\citet{Bouwens15} presented results from a compilation of
observations taken with the Advanced Camera for Surveys (ACS) and
near-infrared Wide Field Camera 3 (WFC3/IR) since 2002 through 2012. 
The survey inclues the following fields of view. XDF,
HUDF09-1, HUDF09-2, CANDELS-S/Deep,  CANDELS-S/Wide, ERS,
CANDELS-N/Deep, CANDELS-N/Wide, CANDELS-UDS,  CANDELS-COSMOS and
CANDELS-EGS.
%The information in that study comes from the ACS and WFC3/IR using the
%filter $B_{435}$, $V_{606}$, $ i_{814}$, $ z_{850}$, $ I_{814}$, $Y_{098}$, $Y_{105}$,
%$J{125}$,  $JH_{140}$ and $H_{160}$.

%with areas of 4.7, 4.7, 4.7, 64.5, 34.2,  40.5, 62.9,
%60.9, 151.2, 151.9 and 150.7 arcmin$^2$ respectively.  
The total survey area is $740.8$ arcmin$^2$ over five different lines
of sight, with a total estimated volume of  $1.8 \times 10^6
\textrm{Mpc}^3$ comoving. 
The limiting magnitude ranges between $\sim27.5$mag in CANDELS-EGS and
$\sim30 $mag in  the  deepest field (XDF). 
The total number of $z=6$ LBG candidates is $940$, most of 
them in the faint end of the LF given the relativeley small survey volume.
The restframe UV magnitudes for these candidates are in the range.
$-22.52\leq M_{1600} \leq -16.77$.
The estimated Schechter parameters:
$\phi^* =(0.33_{-0.10}^{+0.15}) \times 10 ^{-3}  \textrm{Mpc}^{-3} $, 
$M^*_{1600} = -21.16\pm 0.20$ and $\alpha = -1.91 \pm 0.09$. 
%\citet{Bouwens15} notes that only using few fields of view can yield a
%LF with a deviations from the Schechter shape.

@@

The starting point for this method is a population of dark matter halos.
To each halo we assign a UV luminosity according to the following
parameterization.
  \begin{equation}\label{eqn:luminosity}
  L_{\textrm{\small{UV}}} (M) = L_{0} M \left[ \left( \frac{M}{M_0}\right)^{-\beta} 
		   + \left( \frac{M}{M_0}\right)^{\gamma} 
               \right]^{-1},
  \end{equation}
where $M$ is the DM mass, $L_{0}$ is a normalization constant, $M_0$
is the critical mass where the luminosity function has a slope change, 
$\beta$ and $\gamma$ are two slopes corresponding to the faint and
bright end, respectively. 
We now that this equation has the same functional dependence suggested
 by \citet{Moster10} to link stellar and dark matter masses.

@@

Cosmological N-body simulations are the source of the dark matter halo
populations.
We use two different simulations to cover the wide dynamical range
explored by the observations: Big MultiDark Planck (MDPL) and Planck
Bolshoi (P-Bolshoi). 
Both simulations use 2013 Planck cosmology  defined by the following
parameters: $\Omega_M = 0.307$, $\Omega_B = 0.048$, $\Omega_\Lambda =
0.730$, $\sigma_8 = 0.829$, $n_s = 0.96$ and  $H_0 = 67.8$.

The MDPL run is a N-body dark matter only simulation based on the L-Gadget2 
code. 
The simulated volume is a cubic box of $1 \textrm{Gpc h}^{-1}$ on a side.
It has $3840^3$ dark matter particles mass of $1.51\times 9
\textrm{M}_{\odot} \textrm{h}^{-1}$.
The DMH Catalog at $z=6$ contains $\sim 10.9 \times 10^7$   halos, to
avoid incompleteness in the low mass end, halos with mass below
$10^{10.3} \textrm{M}_{\odot} \textrm{h}^{-1}$ are rejected. 
We split this large volume into 64 smaller cubic boxes of $250$\hMpc
on a side (similar volume to the observations by \citet{Willott13}) to
study the influence of cosmic variance.

The P-Bolshoi simulation...

We obtained the data from the public
database\footnote{\url{http://www.multidark.org}} \citep{Riebe13}.

>>>>

\title{The connection between star formation rate and dark matter halo
  mass during reionization}
\shorttitle{SFR and DM halo mass during reionization}

@@

\keywords{galaxies: high-redshift --- methods: numerical} 
\begin{abstract}
We present updated constraints on the relationship between the star
formation rate and dark matter halo mass at redshift $z\sim 6$.
The observational basis for our work is the restframe UV luminosity
function data obtained with HST, CFHTLS, Subary and UKIRT.
The constraints are based on an abundance matching methodology to the
observational data using cosmological N-body simulations assuming a
doible power law relationship between halo mass and star formation
rate follows
We take into account the influence on the results of the dust extinction
scaling derived from observations by Bouwens et al. (2012).
Taking advantage of a wide dynamical range in observations and
simulations we manage to constrain the free parameters of our model
for halos in the mass range $10^{10}\Msun < M_{h}<10^{13}\Msun$. 
We compare our results against the constraints of abundance matching
methods (to the stellar mass), a semi-analytic model of galaxy
formation (GALFORM) and a hydrodynamical simulation (Illustris).
\end{abstract}

@@

We use information compiled in four different publications that select
galaxy candidates at $z\sim 6$ using the drop-out  technique
\citep{Steidel96}.   
In what follows we describe the relevant details of each reference.

\subsection{Bouwens et al. 2015}
\citet{Bouwens15} presented results from a compilation of
observations taken with the Advanced Camera for Surveys (ACS) and
near-infrared Wide Field Camera 3 (WFC3/IR) since 2002 through 2012. 
The survey inclues the following fields of view. XDF,
HUDF09-1, HUDF09-2, CANDELS-S/Deep,  CANDELS-S/Wide, ERS,
CANDELS-N/Deep, CANDELS-N/Wide, CANDELS-UDS,  CANDELS-COSMOS and
CANDELS-EGS.

%with areas of 4.7, 4.7, 4.7, 64.5, 34.2,  40.5, 62.9,
%60.9, 151.2, 151.9 and 150.7 arcmin$^2$ respectively.  
The total survey area is $740.8$ arcmin$^2$ over five different lines
of sight, with a total estimated volume of  $1.8 \times 10^6
\textrm{Mpc}^3$ comoving. 
The limiting magnitude ranges between $\sim27.5$mag in CANDELS-EGS and
$\sim30 $mag in  the  deepest field (XDF). 
The total number of $z=6$ LBG candidates is $940$, most of 
them in the faint end of the LF given the relativeley small survey volume.
The restframe UV magnitudes for these candidates are in the range.
$-22.52\leq M_{1600} \leq -16.77$.
The estimated Schechter parameters:
$\phi^* =(0.33_{-0.10}^{+0.15}) \times 10 ^{-3}  \textrm{Mpc}^{-3} $, 
$M^*_{1600} = -21.16\pm 0.20$ and $\alpha = -1.91 \pm 0.09$.

@@

The starting point for this method is a population of dark matter halos.
To each halo we assign a UV luminosity according to the following
parameterization.
  \begin{equation}\label{eqn:luminosity}
  L_{\textrm{\small{UV}}} (M) = L_{0} M \left[ \left( \frac{M}{M_0}\right)^{-\beta} 
		   + \left( \frac{M}{M_0}\right)^{\gamma} 
               \right]^{-1},
  \end{equation}
where $M$ is the DM mass, $L_{0}$ is a normalization constant, $M_0$
is the critical mass where the luminosity function has a slope change, 
$\beta$ and $\gamma$ are two slopes corresponding to the faint and
bright end, respectively. 
We note that this equation has the same functional dependence suggested
 by \citet{Moster10} to link stellar and dark matter masses.

We also include a fixed intrinsic scatter in the mass to SFR
relationship... %http://arxiv.org/pdf/1507.00999.pdf

@@

Cosmological N-body simulations are the source of the dark matter halo
populations.
We use two different simulations to cover the wide dynamical range
explored by the observations: the Big MultiDark Planck (MDPL) and
Planck-Bolshoi (P-Bolshoi).  
Both simulations use cosmological parameters consistent with 2013
Planck results: $\Omega_M = 0.307$, $\Omega_B = 0.048$, $\Omega_\Lambda =
0.730$, $\sigma_8 = 0.829$, $n_s = 0.96$ and  $H_0 = 67.8$.

The MDPL is a N-body dark matter only simulation ran unsing the
L-Gadget2 code.
The simulated volume is a cubic box of $1000$ \hMpc on a side.
It has $3840^3$ dark matter particles mass of $1.51\times 10^{9}$ \hMsun.
The halo catalog at $z=6$ is built using the Bound Density Maxima algorithm.
We split the simulation volume into 64 smaller cubic boxes of
$250$\hMpc to study the influence of cosmic variance in matching the
observations  by \citet{Willott13}

The P-Bolshoi simulation follows the non-linear evolution of $2048^3$
particles in a cubic box of $250$ \hMpc on a side.
This translates into a mass resolution of $1.35\times 10^{8}$ \hMsun
per particle. We split this simulation into $8$ smaller cubic boxes of
$125$ \hMpc on a side to study cosmic variance in matching the
observations by \citet{McLure09, Finkelstein14, Bouwens15}

To avoid incompleteness in the low mass end we exclude halos with
masses lower than $10^{10.3}$\hMsun.

We obtain the halo catalogs from the public \texttt{cosmosim}
database \footnote{\url{http://www.cosmosim.org}} \citep{Riebe13}.
